---
title: "Summary report for the GPE"
date: "`r format(Sys.time(), '%d %B %Y, %H:%M')`"
output: html_document
---

# The emulator fit
+ This GPE was trained with `r fit$n.train` runs. 

+ The input variables used were: `r colnames(fit$training.inputs)`.  

+ The output variables used were: `r colnames(fit$training.outputs)`.   

+ Below are a few summary statistics of the training inputs and outputs. 

```{r, echo = FALSE, results='asis'}
stargazer::stargazer(cbind(fit$training.inputs, fit$training.outputs), summary = TRUE, 
                     type = "latex", title = "Summary of training data", nobs = FALSE, header=FALSE, iqr = TRUE)
```

<!-- # Prior Mean function -->
+ The mean function used for the prior distribution was:   
`r format(fit$formula)`


```{r, echo=FALSE}
# define correlation function used
if (isTRUE(all.equal(corMatern2.5, fit$cor.function))) {
    cor.funct <- "Matern 2.5"
} else if (isTRUE(all.equal(corGaussian, fit$cor.function))) {
    cor.funct <- "Gaussian"
} else if (isTRUE(all.equal(corGaussianPeriodic, fit$cor.function))) {
    cor.funct <- "Gaussian Periodic"
} else 
    cor.funct <- fit$formula
```

+ The correlation function used in the analysis was:  
`r cor.funct`

```{r, echo=FALSE}
if (!is.null(fit$opt.convergence)) {
    if (fit$opt.convergence == 0) {
        conv <- "optimisation was successful"
    } else if (fit$opt.convergence == 1) {
        conv <- "optimisation reached iteration limit"
    } else 
        conv <- paste("optimisation may not have succeeded - Convergence code:", fit$opt.convergence, "(See ?optim for more details)")
    # conv <- cat("Convergence: ", conv, "\n")
    # if (!is.null(fit$opt.message)) {
    #     cat("Message:", fit$opt.message, "\n")
}

```
+ The `r fit$optim.method` method was used for optimisation. The `r conv`. 

+ The roughness parameters (posterior mean of $\hat\beta$) were calculated as:
```{r, echo = FALSE, results='asis'}
stargazer::stargazer(fit$betahat,
                     type = "latex", title = "posterior mean of $\\hat\\beta$", header=FALSE)
```

+ The sigma square parameter was estimated as:  
```{r, echo = FALSE, results='asis'}
stargazer::stargazer(fit$sigmasq.hat,
                     type = "latex", title = "posterior mean of $\\hat\\sigma^2$", nobs = FALSE, header=FALSE, iqr = TRUE)
```


# Cross validation analysis
+ Leave one out cross validation (LOOCV) was carried out. The following is a plot of the predictions (calculated using LOOCV) against the true output."

```{r, echo = FALSE, fig.show='asis', fig.pos="h"}
CV.fit <- crossVal(fit)
```
+ The root mean square error was calculated as ", `r format(CV.fit$mean.RMSE)`, "and the normalised root mean square error was  `r format(CV.fit$mean.RMSE/(max(fit$training.outputs) - min(fit$training.outputs)))`.  


#Session Info
Please note that the MUCM package version used is `r packageVersion("MUCM")`. 
The package depends on the following packages. The version number indicates the version number of the package being used. 
```{r, echo=FALSE}
installedPackages <- installed.packages()
Package_Name <- unlist(strsplit(installedPackages[which(rownames(installedPackages)=="MUCM"), "Imports", drop = F],", ")[[1]])
version <- vector(mode = "character")
for (i in Package_Name){
    version <- c(version, paste(packageVersion(i)))
}
dependencies <- data.frame("Package Name" = Package_Name, "Package Version" = version)
``` 

```{r, echo = FALSE, results='asis'}
stargazer::stargazer(dependencies, summary = FALSE,
                     type = "latex", title = "Dependencies on the MUCM package", header=FALSE)
```
